---
title: "Untitled"
author: "Sarah Brashear"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(primer.data)
library(rstanarm)

```

## What is the average age of people in Massachusetts? 

```{r}
# Using trains data:
# ?trains

# view(trains)

# For reference, the mean of age is 42ish
# lowest age is 20, highest is 68

# mean(trains$age)
# 42.36522

# Age is an integer 

```

Using Trains data to answer the question.
-Population: Entire Massachusetts population
-Sample: 115 people at commuter train stations
-Ideal Preceptor table has 5 million rows, one for each person, and everyone's 
age included
-Representativeness - connecting our question to the population 
-Problem: everyone in our sample is between 20 and 68, which isn't the full
range of ages in the the whole state of MA
-Survey conducted at commuter train stations - the demographic that uses these
trains may not be perfectly repreresentative of the entire Mass population

```{r}

fit_obj <- stan_glm(data = trains, 
                    formula = age ~ 1, 
                    family = gaussian, 
                    refresh = 0,
                    seed = 10)

```

```{r}

pe <- posterior_epred(object = fit_obj,
                      newdata = tibble(constant = 1)) %>%
  as_tibble()

```

```{r}
pe %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    labs(title = "Posterior for Average Age of People from Massachusetts",
         subtitle = "Average age likely between 40-45 years",
         x = "Average Age",
         y = "Probability",
         caption = "Data source: Trains Data from Primer") + 
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

If you met 10 random people, what would be the difference in age between 2nd oldest and 2nd youngest?

```{r}
newobs <- tibble(constant = rep(1, 10))

pp <- posterior_predict(object = fit_obj,
                        newdata = newobs) %>% 
        as_tibble() %>%
  rowwise() %>% 
  mutate(diff = sort(c_across(), decreasing = FALSE)[9] -
                sort(c_across(), decreasing = FALSE)[2]) 

```

```{r}

pp %>%
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    labs(title = "Posterior for Age Difference",
         subtitle = "Average age likely between 40-45 years",
         x = "Difference in Age between 2nd Oldest and 2nd Youngest",
         y = "Probability",
         caption = "Data source: Trains Data from Primer") + 
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()

# Don't know why we have negative values?
  
```

